Early Observations of the Type Ia Supernova \abc:\\ A Case of Interaction with Nearby, Unbound Material and/or Strong Ejecta Mixing

### 2018-05-22 doc/ms.tex
update abstract

\title{Early Observations of the Type Ia Supernova \abc:\\
a Case of Interaction with Nearby, Unbound Material and/or Strong Ejecta Mixing}

@@

Early observations of Type Ia supernovae (SNe) provide a unique probe of their
progenitor systems and explosion physics. Here, we report the intermediate
Palomar Transient Factory (iPTF) discovery of an extraordinarily young SN Ia,
\abc. By fitting a power law to our early light curve, we infer that first
light for the SN, that is when the SN could have first been detected
by our survey, occurred only $0.15\pm_{0.07}^{0.15}$\,d before our
first detection. In the $\sim$24\,hr after discovery, \abc\ rose by
$\sim$2\,mag, featuring a near-linear rise in flux for $\gtrsim$3 d.
Early spectra show strong \ion{C{2} absorption, which disappears
after $\sim$7\,d.} Unlike the extensively-observed Type Ia SN\,2011fe, the
$(B-V)_0$ colors of \abc\ are blue and nearly constant in the days after
explosion. We show that our early observations of \abc\ cannot be explained by
either SN shock breakout and the associated, subsequent cooling, or the SN
ejecta colliding with a stellar companion. Instead, we argue that the early
characteristics of \abc, including: (i) the rapid, near-linear rise, (ii) the
non-evolving blue colors, and (iii) the strong \ion{C{2}} absorption,
are the result of either ejecta interaction with nearby, unbound
material or vigorous mixing of radioactive $^{56}$Ni in the SN ejecta, or a
combination of the two. In the next few years, dozens of very young
\textit{normal} SNe Ia will be discovered, and observations similar to those
presented here will constrain the white dwarf explosion mechanism.

@@

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{methods: observational --- surveys --- supernovae: general --- supernovae: individual (\abc, SN\,2011fe)}

>>>>

\title{Early Observations of the Type Ia Supernova \abc:\\
A Case of Interaction with Nearby, Unbound Material and/or Strong Ejecta Mixing}

@@

Early observations of Type Ia supernovae (SNe Ia) provide a unique probe of
their progenitor systems and explosion physics. Here we report the
intermediate Palomar Transient Factory (iPTF) discovery of an
extraordinarily young SN Ia, \abc. By fitting a power law to our early light
curve, we infer that first light for the SN, that is when the SN could have
first been detected by our survey, occurred only
$0.15\pm_{0.07}^{0.15}$\,days before our first detection. In the
$\sim$24\,hr after discovery, \abc\ rose by $\sim$2\,mag, featuring a
near-linear rise in flux for $\gtrsim$3\,days. Early spectra show strong
\ion{C}{2} absorption, which disappears after $\sim$7\,days. Unlike the
extensivelyobserved SN Ia SN\,2011fe, the $(B-V)_0$ colors of \abc\ are blue
and nearly constant in the days after explosion. We show that our early
observations of \abc\ cannot be explained by either SN shock breakout and
the associated, subsequent cooling or the SN ejecta colliding with a stellar
companion. Instead, we argue that the early characteristics of \abc,
including (i) the rapid, near-linear rise, (ii) the nonevolving blue colors,
and (iii) the strong \ion{C{2}} absorption, are the result of either ejecta
interaction with nearby, unbound material or vigorous mixing of radioactive
$^{56}$Ni in the SN ejecta, or a combination of the two. In the next few
years, dozens of very young \textit{normal} SNe Ia will be discovered, and
observations similar to those presented here will constrain the white dwarf
explosion mechanism.

@@

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{methods: observational  --- supernovae: general --- supernovae: individual (\abc; SN\,2011fe) --- surveys}
